Copulas and their potential for ecology

### 2019-09-08 Paper.Rmd
adjusting the first pedagog fig

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{(A-D) Bivariate datasets showing diverse relationships between 
variables; many of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. (C, D) Contours 
of probability density functions (pdf) of Clayton (C) and survival-Clayton 
(D) copulas with parameter 5 (see section on methods for Q1), together
with samples from the corresponding distributions. (E,F) Reflections
of C, D, respectively, about a vertical axis. (G) Contours of the
pdf of a normal copula (methods for Q1) with 
parameter chosen to
have the same Spearman correlation as A-D, together with a sample.
(H) The portion of the Spearman correlation within a band 
can be computed
for any band (methods for Q1) to describe how dependence
varies from one part of the two distributions to another. Diagonal lines
show two bands, the data in the left/lower band showing stronger
dependence than the right/upper band.
Subscripts h and v 
stand for "horizontal" and "vertical". \label{fig_cop_pedag1}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{Bivariate datasets showing diverse relationships between 
variables; some of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. Subscripts h and v 
in the axis labels stand for "horizontal" and "vertical".\label{fig_cop_pedag1}}
\end{center}
\end{figure}
<!--***DAN: When I cut panels out of this figure (saving them for use in a 
later figure), I also cut the caption, and here is the cut stuff for later use:
(C, D) Contours 
of probability density functions (pdf) of Clayton (C) and survival-Clayton 
(D) copulas with parameter 5 (see section on methods for Q1), together
with samples from the corresponding distributions. (E,F) Reflections
of C, D, respectively, about a vertical axis. (G) Contours of the
pdf of a normal copula (methods for Q1) with 
parameter chosen to
have the same Spearman correlation as A-D, together with a sample.
(H) The portion of the Spearman correlation within a band 
can be computed
for any band (methods for Q1) to describe how dependence
varies from one part of the two distributions to another. Diagonal lines
show two bands, the data in the left/lower band showing stronger
dependence than the right/upper band.
Subscripts h and v 
stand for "horizontal" and "vertical".
-->
